---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FloraIberica

<!-- badges: start -->
<!-- badges: end -->

`FloraIberica` R package facilitates checking taxonomic and distribution data for the c. 6500 vascular plants present in the Iberian Peninsula and Balearic Islands, based on the [AFLIBER database](https://doi.org/10.1111/geb.13363).

## Installation

``` r
remotes::install_github("Pakillo/FloraIberica")
```

## Usage

```{r example}
library(FloraIberica)
```

### Checking if taxa are present

```{r}
is_present(genus = "Laurus", species = c("nobilis", "azorica"))
```

### Checking if taxa are endemic

```{r}
is_endemic(genus = "Aconitum", species = "napellus", 
           subspecies = c("castellanum", "lusitanicum"))
```

### Getting the distribution of plant taxa

Returns sf or dataframe:

```{r}
get_distribution("Abies", "pinsapo")
```


### Making distribution maps

#### Single taxon

```{r}
map_distribution(genus = "Laurus", species = "nobilis")
```


#### Many taxa

Distribution of Iberian *Abies*:

```{r}
abies <- get_distribution("Abies")
map_distribution(abies)
map_distribution(abies, facet = TRUE, ncol = 1)
map_distribution(abies, taxo.level = "genus")
```

Iberian Pines: 

```{r}
pinus <- get_distribution("Pinus")
library(ggplot2)
map_distribution(pinus, facet = TRUE, ncol = 2) + 
  theme(axis.text = element_text(size = 6))
```


## Citation

```{r results='asis', cache = FALSE}
print(citation("FloraIberica"), style = "text")
```


