---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FloraIberica

<!-- badges: start -->
<!-- badges: end -->

FloraIberica facilitates checking taxonomic and distribution data for the c. 6500 vascular plant species present in the Iberian Peninsula and Balearic Islands, based on the [AFLIBER database](https://doi.org/10.1111/geb.13363).

## Installation

You can install the development version of FloraIberica like so:

``` r
remotes::install_github("Pakillo/FloraIberica")
```

## Examples

```{r example}
library(FloraIberica)
```

### Checking if taxa are present

```{r}
is_present(genus = "Laurus", species = c("nobilis", "azorica"))
```

### Checking if taxa are endemic

```{r}
is_endemic(genus = "Aconitum", species = "napellus", 
           subspecies = c("vulgare", "castellanum", "lusitanicum"))
```

### Getting the distribution of plant taxa

```{r}
get_distribution("Abies", "pinsapo")
```


### Making distribution maps

#### Single taxon

```{r}
laurus.sf <- get_distribution("Laurus", "nobilis")
map_distribution(laurus.sf)
```


#### Many taxa

Iberian *Abies*: 

```{r}
abies.sf <- get_distribution("Abies")
map_distribution(abies.sf)
map_distribution(abies.sf, facet = TRUE, ncol = 1)
```

Iberian Pines: 

```{r}
library(ggplot2)
pinus <- get_distribution("Pinus")
mapa <- map_distribution(pinus, facet = TRUE, ncol = 2)
mapa + theme(axis.text = element_text(size = 6))

```


## Citation

```{r results='asis', cache = FALSE}
print(citation("FloraIberica"), style = "text")
```

